---
title: "Maltreatment_Project_TP"
author: "Tom Price"
date: "12.04.21"
output:
  html_document: default
  pdf_document: default
---


# Set markdown options
```{r setup}
knitr::opts_chunk$set(echo = TRUE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)
```

# Clear workspace
```{r clear workspace}
remove(list = ls())
```


# Retrieve the recent date
```{r recent date}
date = Sys.Date()
date
```

## Install Packages
```{r Install Packages}
#install.packages("knitr")
#install.packages("broom")
#install.packages("summarytools")
#install.packages("psych")
#install.packages("polycor")
#install.packages("gt")
#install.packages("skimr")
#install.packages("tidyverse")
#install.packages("kableExtra")
#install.packages("freqtables")
```

## Load Packages
```{r Load Packages}
library(knitr)
library(broom)
library(summarytools)
library(psych)
library(polycor)
library(gt)
library(skimr)
library(kableExtra)
library(freqtables)
library(tidyverse)
```


# Define colours for plotting
```{r GLAD colour palette}
glad_palette = c("#efc00b", "#b7dee8")
palette=glad_palette
```

# Add_numeric function
```{r numeric conversion function}
#Function used to convert character variables into numeric variables.
add_numeric <- function(dat,exclude_numeric = "ID") {
  exclude <- sapply(dat, function(col) {
any(is.na(attr(col, "labels")))
  })
exclude_col <- colnames(dat)[exclude]
dat_fct <- dat
dat_fct[!colnames(dat_fct) %in% exclude_col] <- 
sjlabelled::as_label(dat_fct[!colnames(dat_fct) %in% exclude_col])
dat_fct_num <- dat[!colnames(dat) %in% c(exclude_col,exclude_numeric)]
colnames(dat_fct_num) <- paste(colnames(dat_fct_num), "numeric", sep = "_")
 return(bind_cols(dat_fct, dat_fct_num))
} 

```

# Read in individual questionnaires
## Demographics
```{r Demographics read in data}
dem.glad.1 <- readRDS("../../data_raw/16.04.2021/dem_glad.rds")
dim(dem.glad.1)

#dem.glad.1$startDate <- NULL
#dem.glad.1$endDate <- NULL

colnames(dem.glad.1)
```

Summary demographics file
```{r demographics summary before recoding}
dem.glad.1 %>%
  select(
    age = dem.how_old_are_you_now.txt,
    sex = dem.select_questionnaire_items_medical,
    gender = dem.which_gender_do_you_identify_with,
    transgender = dem.do_you_identify_as_transgender,
    ethnicity = dem.questions_based_ethnic_origin, 
    sexuality = dem.what_is_your_sexual_orientation,
    degree = dem.college_or_university_degree,   
    uppersixth = dem.a_levelsas_levels_or_equivalent,  
    years_in_education = dem.school_education_school_years.txt,
    employment = dem.what_is_your_current_employment_status,
    marital_status = dem.what_is_your_current_maritalrelationship_status,
    pregnant_ever = dem.have_you_ever_been_pregnant,     
    degree = dem.college_or_university_degree,
    dem_current_cm = dem.what_is_your_current_height,
    dem_current_ft = dem.what_is_your_current_height.1,
    dem_current_in = dem.what_is_your_current_height.2,
    dem_current_kg = dem.current_weight_pregnant_weight,
    dem_current_st = dem.current_weight_pregnant_weight.1,
    dem_current_lb = dem.current_weight_pregnant_weight.2
  ) %>%
  skim()
```

Select variables and read them in to single rds
```{r demographics select variables}
dem.glad.1.id <- dem.glad.1 %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE)  %>%
  select(
    ID = externalDataReference,
        startDate,
    endDate,
    age = dem.how_old_are_you_now.txt,
    sex = dem.select_questionnaire_items_medical,
    gender = dem.which_gender_do_you_identify_with,
    transgender = dem.do_you_identify_as_transgender,
    ethnicity = dem.questions_based_ethnic_origin, 
    sexuality = dem.what_is_your_sexual_orientation,
    degree = dem.college_or_university_degree,   
    uppersixth = dem.a_levelsas_levels_or_equivalent,  
    years_in_education = dem.school_education_school_years.txt,
    employment = dem.what_is_your_current_employment_status,
    marital_status = dem.what_is_your_current_maritalrelationship_status,
    pregnant_ever = dem.have_you_ever_been_pregnant,     
    degree = dem.college_or_university_degree,
    dem_current_cm = dem.what_is_your_current_height,
    dem_current_ft = dem.what_is_your_current_height.1,
    dem_current_in = dem.what_is_your_current_height.2,
    dem_current_kg = dem.current_weight_pregnant_weight,
    dem_current_st = dem.current_weight_pregnant_weight.1,
    dem_current_lb = dem.current_weight_pregnant_weight.2) %>%
  add_numeric() %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor,  ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(dem.glad.1.id)

#Differences
dim(dem.glad.1)[1]-dim(dem.glad.1.id)[1]
```

Demographics selected
```{r Demographics double check}
skim(dem.glad.1.id)
```

## Mental Health Diagnoses
```{r Mentalh health diagnoses read in data}
mhd.glad.1 <- readRDS("../../data_raw/16.04.2021/mhd_glad.rds")
dim(mhd.glad.1)

mhd.glad.1$startDate <- NULL
mhd.glad.1$endDate <- NULL

colnames(mhd.glad.1)
```

Summary mental health file
```{r mental health summary before recoding}
mhd.glad.1 %>%
  select(
    mhd.an,
    mhd.atypical_an,
    mhd.bn,
    mhd.bed) %>%
  skim()
```

Select variables and read them in to single rds
```{r mental health select variables}
exclude_cols_dem <- c("ID",
                  "startDate",
                  "endDate_GLAD")

mhd.glad.1.id <- mhd.glad.1 %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE)  %>%
  select(
         ID = externalDataReference, # ID
         #mhd.mdd,
         #mhd.perinatal_depression,
         #mhd.pmdd,
         #mhd.bipolar_disorder,
         #mhd.gad,
         #mhd.social_anxiety,
         #mhd.specific_phobia,
         #mhd.agoraphobia,
         #mhd.panic_disorder,
         #mhd.panic_attacks,
         #mhd.ptsd,
         #mhd.ocd,
         #mhd.bdd,
         #mhd.other_ocd,
         #mhd.dont_know,
         #mhd.prefer_not_to_answer,
         mhd.an,
         mhd.atypical_an,
         mhd.bn,
         mhd.bed,
         #mhd.schizophrenia,
         #mhd.schizoaffective,
         #mhd.psychosis,
         #mhd.personality_disorder,
         #mhd.asd,
         #mhd.addadhd,
         #mhd.other,
         #mhd.personality_disorder_diagnosed
         ) %>%
  add_numeric() %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(mhd.glad.1.id)

#Differences
dim(mhd.glad.1)[1]-dim(mhd.glad.1.id)[1]
```

Mental health diagnoses selected
```{r Mental health diagnoses double check}
skim(mhd.glad.1.id)
```


## CTS: Childhood Maltreatment (CM)
Maltreatment was measured using the childhood maltreatment screener (CTS; Glaesmer et al., 2013)
```{r CTS read in data}
CTS.glad.1 <- readRDS("../../data_raw/16.04.2021/cts_glad.rds")
dim(CTS.glad.1)

CTS.glad.1$startDate <- NULL
CTS.glad.1$endDate <- NULL

colnames(CTS.glad.1)
```

Double checking what happens if a participant skip the questionnaire
```{r Double checking what happens if a participant skip the questionnaire}
CTS.glad.1 %>%
  filter(cts.visit_www_skip_button == 0) %>%
  head()
```

Number of participants that skipped the CTS questionnaire
```{r Number of participants that skipped the CTS questionnaire}
CTS.glad.1 %>%
  filter(cts.visit_www_skip_button == 0) %>%
  nrow()
```
449 elected to skip the CTS questionnaire in response to the item: '‘This section asks about your childhood and some possible stresses and strains of life. If this is too difficult, then please use the skip button below.’ 

Summary maltreatment file
```{r CTS summary before recoding}
CTS.glad.1 %>%
  select(
    CEN = cts.i_felt_loved,
    CEA = cts.felt_family_hated,
    CPN = cts.needed_doctor,
    CPA = cts.family_hit_bruises_left,
    CSA = cts.someone_molested_me
  ) %>%
  skim()
```

Select variables and read them in to single rds
```{r CTS select variables}
CTS.glad.1.id <- CTS.glad.1 %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE)  %>%
  select(
    ID = externalDataReference, # ID
         CEN = cts.i_felt_loved,
         CEA = cts.felt_family_hated,
         CPN = cts.needed_doctor,
         CPA = cts.family_hit_bruises_left,
         CSA = cts.someone_molested_me)  %>%
  add_numeric() %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(CTS.glad.1.id)

#Differences
dim(CTS.glad.1)[1]-dim(CTS.glad.1.id)[1]
```

Childhood maltreatment variables selected
```{r CTS double check}
skim(CTS.glad.1.id)
```

## Patient health questionnaire - 9 (PHQ-9)
Current depression syptoms were measured using the PHQ-9
```{r PHQ-9 read in data}
PHQ9.glad.1 <- readRDS("../../data_raw/16.04.2021/phq9_glad.rds")
dim(PHQ9.glad.1)

#PHQ9.glad.1$startDate <- NULL
#PHQ9.glad.1$endDate <- NULL

colnames(PHQ9.glad.1)
```

Summary PHQ-9 file
```{r PHQ-9 summary before recoding}
PHQ9.glad.1 %>%
  select(
    phq9.little_interest_or_pleasure_in_doing_things,
    phq9.feeling_down_depressed_or_hopeless,         
    phq9.staying_asleep_sleeping_trouble,          
    phq9.feeling_tired_or_having_little_energy,      
    phq9.poor_appetite_or_overeating,             
    phq9.feeling_bad_failure_family,                 
    phq9.trouble_concentrating_reading_newspaper,    
    phq9.moving_fidgety_noticed_opposite,          
    phq9.dead_hurting_thoughts
  ) %>%
skim()
```

Select variables and read them in to single rds
```{r PHQ-9 select variables}
PHQ9.glad.1.id <- PHQ9.glad.1 %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE)  %>%
  select(
 #   ID = externalDataReference, # ID hashed out to merge on startDate and endDate
    startDate,
    endDate,
         phq9.little_interest_or_pleasure_in_doing_things,
         phq9.feeling_down_depressed_or_hopeless,         
         phq9.staying_asleep_sleeping_trouble,          
         phq9.feeling_tired_or_having_little_energy,      
         phq9.poor_appetite_or_overeating,             
         phq9.feeling_bad_failure_family,                 
         phq9.trouble_concentrating_reading_newspaper,    
         phq9.moving_fidgety_noticed_opposite,          
         phq9.dead_hurting_thoughts)  %>%
  add_numeric() %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(PHQ9.glad.1.id)

#Differences
dim(PHQ9.glad.1)[1]-dim(PHQ9.glad.1.id)[1]
```

PHQ-9 selected
```{r PHQ-9 double check}
skim(PHQ9.glad.1.id)
```

## Generalised Anxiety Disorder Assessment (GAD-7)
Current anxiety symptoms were measured using the GAD-7
```{r GAD-7 read in data}
GAD7.glad.1 <- readRDS("../../data_raw/16.04.2021/gad7_glad.rds")
dim(GAD7.glad.1)

#GAD7.glad.1$startDate <- NULL
#GAD7.glad.1$endDate <- NULL

colnames(GAD7.glad.1)
```

Summary GAD-7 file
```{r GAD-7 summary before recoding}
GAD7.glad.1 %>%
  select(
    gad7.feeling_nervous_anxious_or_on_edge,
    gad7.control_worrying_stop,         
    gad7.worrying_too_much_about_different_things,          
    gad7.trouble_relaxing,      
    gad7.sit_restless_hard,             
    gad7.becoming_easily_annoyed_or_irritable,                 
    gad7.awful_feeling_afraid_happen
  ) %>%
skim()
```

Select variables and read them in to single rds
```{r GAD-7 select variables}
GAD7.glad.1.id <- GAD7.glad.1 %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE)  %>%
  select(
#    ID = externalDataReference, # ID hashed out to merge on startDate and endDate
        startDate,
    endDate,
         gad7.feeling_nervous_anxious_or_on_edge,
         gad7.control_worrying_stop,         
         gad7.worrying_too_much_about_different_things,          
         gad7.trouble_relaxing,      
         gad7.sit_restless_hard,             
         gad7.becoming_easily_annoyed_or_irritable,                 
         gad7.awful_feeling_afraid_happen)  %>%
  add_numeric() %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(GAD7.glad.1.id)

#Differences
dim(GAD7.glad.1)[1]-dim(GAD7.glad.1.id)[1]
```

GAD-7 selected
```{r GAD-7 double check}
skim(GAD7.glad.1.id)
```

## PTSD Checklist (PCL-6) - six item version
Current Post-Traumatic Stress Symptoms were measured using the PCL-6
```{r PCL-6 read in data}
PCL.glad.1 <- readRDS("../../data_raw/16.04.2021/pcl6_glad.rds")
dim(PCL.glad.1)

PCL.glad.1$startDate <- NULL
PCL.glad.1$endDate <- NULL

colnames(PCL.glad.1)
```

Summary PCL-6 file
```{r PCL-6 summary before recoding}
PCL.glad.1 %>%
  select(
    pcl6.stressful_experience_repeated_images,
    pcl6.stressful_experience_upset_reminded,
    pcl6.stressful_situation_avoiding_activities,
    pcl6.cut_people_feeling_distant,
    pcl6.feeling_irritable_or_having_angry_outbursts,
    pcl6.difficulty_concentrating
  ) %>%
skim()
```

Select variables and read them in to single rds
```{r PCL-6 select variables}
PCL.glad.1.id <- PCL.glad.1 %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE)  %>%
  select(
    ID = externalDataReference, # ID
    pcl6.stressful_experience_repeated_images,
    pcl6.stressful_experience_upset_reminded,
    pcl6.stressful_situation_avoiding_activities,
    pcl6.cut_people_feeling_distant,
    pcl6.feeling_irritable_or_having_angry_outbursts,
    pcl6.difficulty_concentrating)  %>%
  add_numeric() %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(PCL.glad.1.id)

#Differences
dim(PCL.glad.1)[1]-dim(PCL.glad.1.id)[1]
```

PCL-6 selected
```{r PCL-6 double check}
skim(PCL.glad.1.id)
```

## Work and social adjustment (WSAS)
```{r WSAS read in data}
WSAS.glad.1 <- readRDS("../../data_raw/16.04.2021/wsas_glad.rds")
dim(WSAS.glad.1)

WSAS.glad.1$startDate <- NULL
WSAS.glad.1$endDate <- NULL

colnames(WSAS.glad.1)
```

Summary WSAS file
```{r WSAS summary before recoding}
WSAS.glad.1 %>%
  select(
    wsas.areretired_becauseof_choose_job,
    wsas.home_management_impaired_problem,
    wsas.impaired_problem_social_leisure,
    wsas.impaired_problem_private_leisure,
    wsas.maintain_close_relationships_form
  ) %>%
  skim()
```

Select variables and Read them in to single rds
```{r WSAS select variables}
WSAS.glad.1.id <- WSAS.glad.1 %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE)  %>%
  select(
    ID = externalDataReference, # ID
         wsas.areretired_becauseof_choose_job,
         wsas.home_management_impaired_problem,
         wsas.impaired_problem_social_leisure,
         wsas.impaired_problem_private_leisure,
         wsas.maintain_close_relationships_form)  %>%
  add_numeric() %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(WSAS.glad.1.id)
# Inspect colnames
#colnames(WSAS.glad.1.id)
#Differences
dim(WSAS.glad.1)[1]-dim(WSAS.glad.1.id)[1]
```

WSAS selected
```{r WSAS double check}
skim(WSAS.glad.1.id)
```

## Alcohol Use Disorders Identification Test (AUDIT)
```{r AUDIT read in data}
AUDIT.glad.1 <- readRDS("../../data_raw/16.04.2021/audit_glad.rds")
dim(AUDIT.glad.1)

AUDIT.glad.1$startDate <- NULL
AUDIT.glad.1$endDate <- NULL

colnames(AUDIT.glad.1)
```

Summary AUDIT file

"audit.stop_drinking_found_started_numeric", # How often during the last year have you found that you were not able to stop drinking once you had started?
"audit.expected_failed_drinking_year_numeric", # How often during the last year have you failed to do what was normally expected from you because of drinking?
"audit.morning_needed_drink_year_numeric", # How often during the last year have you needed a first drink in the morning to get yourself going after a heavy drinking session?
"audit.guilt_remorse_drinking_feeling_numeric", # How often during the last year have you had a feeling of guilt or remorse after drinking?
"audit.remember_unable_night_happened_numeric", # How often during the last year have you been unable to remember what happened the night before because you had been drinking?
"audit.injured_result_drinking_numeric", # Have you or someone else been injured as a result of your drinking?
"audit.concerned_cut_suggested_relative_numeric", # Has a relative or friend or a doctor or another health worker been concerned about your drinking or suggested you cut down?
"audit.occasion_units_numeric", # How often do you have six or more units on one occasion?
"audit.alcohol_drink_numeric", # How often do you have a drink containing alcohol?
"audit.units_alcohol_drink_drinking_numeric" # How many units of alcohol do you drink on a typical day when you are drinking?

```{r AUDIT summary before recoding}
AUDIT.glad.1 %>%
  select(
    audit.occasion_units,                        
    audit.stop_drinking_found_started,              
    audit.expected_failed_drinking_year,            
    audit.morning_needed_drink_year,                
    audit.guilt_remorse_drinking_feeling,           
    audit.remember_unable_night_happened,           
    audit.injured_result_drinking,                  
    audit.concerned_cut_suggested_relative,         
    #audit.drinking_habits_commented_age.txt,        
    #audit.units_life_drink_alcohol,                 
    audit.alcohol_drink,                            
    audit.units_alcohol_drink_drinking,             
    #audit.substances_highs_legal,                   
    #audit.how_often_do_you_take_it
  ) %>%
  skim()
```

Select variables and read them in to single rds
```{r AUDIT select variables}
AUDIT.glad.1.id <- AUDIT.glad.1 %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE)  %>%
  select(
    ID = externalDataReference, # ID
          audit.occasion_units,                        
          audit.stop_drinking_found_started,              
          audit.expected_failed_drinking_year,            
          audit.morning_needed_drink_year,                
          audit.guilt_remorse_drinking_feeling,           
          audit.remember_unable_night_happened,           
          audit.injured_result_drinking,                  
          audit.concerned_cut_suggested_relative,         
          #audit.drinking_habits_commented_age.txt,        
          #audit.units_life_drink_alcohol,                 
          audit.alcohol_drink,                            
          audit.units_alcohol_drink_drinking,             
          #audit.substances_highs_legal,                   
          #audit.how_often_do_you_take_it
    )  %>%
  add_numeric() %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(AUDIT.glad.1.id)

#Differences
dim(AUDIT.glad.1)[1]-dim(AUDIT.glad.1.id)[1]
```

AUDIT selected
```{r AUDIT double check}
AUDIT.glad.1.id %>%
skim()
```

# Looking at ID Errors
```{r Comparing dem and PHQ9}
x <- dem.glad.1.id[dem.glad.1.id$ID %in% PHQ9.glad.1$externalDataReference,]

length(unique(x$ID))
```
None of the IDs in the dem.glad.1.id tibble match the IDs in PHQ9.glad.1

# Merge DEM, PHQ9, GAD7 on startDate and endDate
We merge those tibbles on startDate and endDate because the IDs are not matching. This must be a data export error (see chunk above).
For this purpose, we create a list object with the three tibbles
```{r list to merge DEM PHQ and GAD}
df_list_dem_phd_gad <- list(
  dem.glad.1.id,
  GAD7.glad.1.id,
  PHQ9.glad.1.id
)
```

Joining of the three questionnaires based on startDate and endDate
```{r join df_list_dem_phd_gad}
DEM.PHQ.GAD.data_merged <- plyr::join_all(
  df_list_dem_phd_gad,
  by = c(
    "startDate",
    "endDate",
    "startDate_numeric",
    "endDate_numeric")
    )
```

Check there are no duplicate columns
```{r Inspect colnames}
DEM.PHQ.GAD.data_merged %>%
  colnames()
```

Check new DEM.PHQ.GAD.data_merged tibble
```{r DEM.PHQ.GAD.data_merged check tiblle of variables to merge on date, include=FALSE}
DEM.PHQ.GAD.data_merged$startDate <- NULL
DEM.PHQ.GAD.data_merged$startDate_numeric <- NULL
DEM.PHQ.GAD.data_merged$endDate <- NULL
DEM.PHQ.GAD.data_merged$endDate_numeric <- NULL

DEM.PHQ.GAD.data_merged 
```

# Merging of the rest of the tibbles
Create a list of the data frames for merging: mhd, CTS, PCL, WSAS, AUDIT
```{r tibble list to merge}
df_list <- list(
  DEM.PHQ.GAD.data_merged,
  mhd.glad.1.id,
  CTS.glad.1.id,
  PCL.glad.1.id,
  WSAS.glad.1.id,
  AUDIT.glad.1.id
  )
```

## Merge the rest of the tibbles
```{r merge data frame, include=FALSE}
CM.data_merged <- plyr::join_all(
  df_list,
  by = c("ID")
    )


#look at the data
nrow(CM.data_merged)
colnames(CM.data_merged)
```

Check if there are duplicates in your data frame after merging
```{r duplicates in your data frame after merging}
CM.data_merged[duplicated(as.list(CM.data_merged))]
```

Inspection of data after complete merge
```{r Inspection of data after complete merge, include=FALSE}
skim(CM.data_merged)
```

# Quality check of tibble
Check if the data frame contains -88, -99, -77, "Seen but not answered", "Don't know", "Prefer not to say", "Prefer not to answer"
```{r Check for non-respones levels}
CM.data_merged %>%
  filter_all(
    any_vars(. %in% c(
      -88,
      -99,
      -77,
      "Seen but not answered",
      "Don't know",
      "Prefer not to say",
      "Prefer not to answer"
      )
      )
    )
```

# Exclusion
## Duplicates
Identify duplicates in tibble
The chunk creates a column in the tibble with TRUE if the ID is duplicated and FALSE is the ID is unique
```{r Identify duplicates in tibble}
CM.data_merged$ID.dup <- duplicated(CM.data_merged$ID)

summary(as.factor(CM.data_merged$ID.dup))
```
All IDs are unique

Number of duplicates
```{r Number of duplicates}
data_complete.dup <- CM.data_merged %>%
  filter(ID.dup == TRUE)

data_complete.dup %>%
  nrow()
```

Number of unique participants
```{r Number of unique participants}
data_complete.raw <- CM.data_merged %>%
  filter(ID.dup == FALSE)

data_complete.raw %>%
  nrow()
```
There are no duplicates in the data set.

## Sex
### Remove participants who do not report their biological Sex
```{r Remove participants that do not report their biological Sex}
dim(data_complete.raw)

data_complete.after_sex_exclusion <- data_complete.raw %>%
  drop_na(sex)

nrow(data_complete.raw)-nrow(data_complete.after_sex_exclusion)
```
754 participants did not report biological sex and therefore were excluded

## Age
### Remove participants who do not report their age
```{r Remove participants that do not report their age}
dim(data_complete.after_sex_exclusion)

data_complete.after_sex_age_exclusion <- data_complete.after_sex_exclusion %>%
  drop_na(age)

nrow(data_complete.after_sex_exclusion)-nrow(data_complete.after_sex_age_exclusion)
```
0 participants did not report age and therefore were excluded

## Any item on the CTS is NA
### Remove participants who do not respond to the CTS
```{r CTS exclusion}
dim(data_complete.after_sex_age_exclusion)

data_complete.after_sex_age_CTS_exclusion <- data_complete.after_sex_age_exclusion %>%
  drop_na(
      "CEN",
      "CEA",
      "CPN",
      "CPA",
      "CSA"
    )

nrow(data_complete.after_sex_age_exclusion)-nrow(data_complete.after_sex_age_CTS_exclusion)
```
5647 participants did not compelte the CTS and therefore were excluded

# Copy data frame
```{r make a copy of data frame after correction}
CM_ED_Data <- data_complete.after_sex_age_CTS_exclusion

dim(CM_ED_Data)
```

# Export
Export the tibble as rds file
```{r Export tibble to rds file}
write_rds(
  x = CM_ED_Data,
  file = paste0("../../data_clean/CM_ED_Data",date,".rds")
)
```
